Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-15 main.tex
Update on Overleaf.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
\caption{The separation (in dex) of each star's oxygen fraction from the median value of the gas phase oxygen mass fraction PDF for the CNM at within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial enrichment period, or 100~Myr.}
\label{fig:stars}
\end{figure}
